RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-03-01 assets/illustration/time_structure.tex
:triangular_flag_on_post: JSAC 230301

	% AmBC/SR
	\foreach \x in {0,...,7}{
			\draw[teal,fill=teal!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,15}{
			\draw[teal,fill=teal!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,1}{
			\draw[teal,ultra thick] (4*\x,3) rectangle ++(4,0.25);
		}
	\draw[latex-latex] (0,3.35) -- (4,3.35) node[above,midway]{BB};
	\draw[latex-latex] (0,2.9) -- (0.5,2.9) node[below,midway]{PB};
	\node at (-1.5,3.125) {AmBC/SR};

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}
	\draw[red,ultra thick] (0,2) rectangle ++(8,0.25);
	\draw[latex-latex] (0,2.35) -- (8,2.35) node[above,midway]{CB};
	\draw[latex-latex] (0,1.9) -- (0.5,1.9) node[below,midway]{PB};
	\node at (-1.5,2.125) {RIS};

	% RIScatter
	\foreach \x in {0,...,3}{
			\draw[brown,fill=brown!25!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,15}{
			\draw[brown,fill=brown!25!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,3}{
			\draw[brown,ultra thick] (2*\x,1) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,1.35) -- (2,1.35) node[above,midway]{BB};
	\draw[latex-latex] (0,0.9) -- (0.5,0.9) node[below,midway]{PB};

>>>>

	% AmBC/SR
	\foreach \x in {0,...,7}{
			\draw[teal,fill=teal!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,15}{
			\draw[teal,fill=teal!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,1}{
			\draw[teal,ultra thick] (4*\x,3) rectangle ++(4,0.25);
		}
	\draw[latex-latex] (0,3.35) -- (4,3.35) node[above,midway]{BB};
	\draw[latex-latex] (0,2.9) -- (0.5,2.9) node[below,midway]{PB};
	\node at (-1.5,3.125) {AmBC/SR};

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}
	\draw[red,ultra thick] (0,2) rectangle ++(8,0.25);
	\draw[latex-latex] (0,2.35) -- (8,2.35) node[above,midway]{CB};
	\draw[latex-latex] (0,1.9) -- (0.5,1.9) node[below,midway]{PB};
	\node at (-1.5,2.125) {RIS};

	% RIScatter
	\foreach \x in {0,...,3}{
			\draw[brown,fill=brown!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,15}{
			\draw[brown,fill=brown!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,3}{
			\draw[brown,ultra thick] (2*\x,1) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,1.35) -- (2,1.35) node[above,midway]{BB};
	\draw[latex-latex] (0,0.9) -- (0.5,0.9) node[below,midway]{PB};
